---
title: "vignettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# shapeR

shapeR aims to simplify GIS mapping by giving access through simple R functions to maps from different sources. 

The list of available maps is shown in the following table:

| Regions   | Sources                                |
|-----------|----------------------------------------|
| World     | <https://www.naturalearthdata.com/>    |
| Countries | <https://gadm.org/download_world.html> |
|           |                                        |

## Installation

You can install the released version of 'shapeR' from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("shapeR")
```

Or you can install the current development version of ‘shapeR’ with:

``` r
install.packages("devtools")
devtools::install_github("warint/shapeR")
```

## How-To

### Step 1: Getting the country’s ISO code

A user needs to enter the ISO code of a country. To have access to this code, the following function provides this information.

```{r,eval=FALSE}
shaper_country() # A list of all countries will be produced

shaper_country(country = "Canada") # The ISO code for Canada will be produced

shaper_country("Canada") # The ISO code for Canada will be produced
```

### Step 2: Choosing the shapefile's level of granularity

Users can visualize which level is available for the choosen country here: <https://gadm.org/download_country_v3.html>

The level goes from 1 to 5, with 0 being the country level. You can access the metadata here: <https://gadm.org/metadata.html>

Be aware that not all countries have the five levels of granularity.

### Step 3: Getting the data

Once the user knows the ISO code and the wanted level, s.he can collect the data in a very easy way through this function:

```{r,eval=FALSE}
shaper_data(country_code = "CAN") # The shapefile for Canada with level 0 (the default) will be produced

shaper_data(country_code = "CAN", level = 3) # The shapefile for Canada with level 3 will be produced

shaper_data("CAN", 3) # The shapefile for Canada with level 3 will be produced
```

## Acknowledgments

The author would like to thank the Center for Interuniversity Research and Analysis of Organizations (CIRANO, Montreal) for its support, as well as Thibault Senegas, Marine Leroi, Martin Paquette and Anne Sophie Gill at SKEMA Global Lab in AI. The usual caveats apply.

